Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-04-23 analyses/scripts/orv_sys_rev_supplementary.Rmd
Rephrased "articles" to "studies"

#Print table of results
knitr::kable(continents_studied_by_count %>% arrange(desc(percentage)),
             col.names = c('Continent',
                           'Number of papers',
                           'Percentage'
                           ),
             caption = 'Number/percent of studies by continent'
             )

>>>>

#Print table of results
knitr::kable(continents_studied_by_count %>% arrange(desc(percentage)),
             col.names = c('Continent',
                           'Number of studies',
                           'Percentage'
                           ),
             caption = 'Number/percent of studies by continent'
             )
